---
title: "W_UP_01"
author: "Iven Santos"
date: "Summer 2022"
output: html_document
---



The report structure should include five sections.  see below



```{r include=FALSE,echo=FALSE}
require(tigerstats)
require(tidyverse)
mydata <- read.csv(file="pushups.csv")
```

# Introduction

<!--In this section you explain what you are trying to show. Where did the data come from? What is the research or other question you are trying to answer?!-->

Create an Rstudio project in your shared space on rstudio.cloud.  Using the dataset called pushups from the tigerstats package in R; answer the question posed by this null and alternate hypothesis in an html markdown document.

$H_0$: There is no difference between the average number of pushups of line vs skill players

$H_A$: The average number of pushups done by line players is statistically different than that of skill players.

# Methods

<!--Decide on your methods: use "variable analysis" or other appropriate descriptors. Make sure to choose at least one graphical method and at least one numerical method.!-->
positions are a categorical variable. Push-ups is a numerical variable. I will do an analysis that explains push-ups based on position
# Results

<!--Divide this section into two sub-sections: One for your descriptive results and one for your inferential results.!-->

## Descriptive Results

### Graphical Descriptive Results
```{r}
boxplot(pushups~position,data=mydata)
```
<!--Graphical results here. Make sure to show your code. Provide appropriate labels for axes, giving units if possible, and provide a good title for the graph, too. Use the graphical results to describe the patterns if any that exist in the data as focused toward the research question!-->


There is push-ups on the y-axis of the box plot. While there is the positions on the x-axis. On the box plot,there is a large segment on each whisker plot. The average push-ups for the positions appears to be different. The skill position appears to do more push-ups based off of the y-axis (pushups)

### Numerical Descriptive Results
```{r}
favstats(pushups~position,data=mydata)
```


<!--Numerical results go here. Use the numerical results to describe the patterns if any that exist in the data as focused toward the research question!-->


The median for both position has a very big difference. It appears the median for the skill position is higher then the line positions. The max the line position can do is 34 push ups while the skill can do up to 108. From the data results it seems that skill positions is far more capable to do the most push ups.

## Inferential Results
```{r}
t.test(pushups~position,data=mydata)
```


<!--State hypothesis clearly. Make sure your discussion of the inferential test covers all the aspects that the test output produces, such as test statistic, p-value etc. Make a decision about the null hypothesis, explain the assumptions on which the selected test/procedure was based, and why the chosen procedure satisfys the assumptions and is appropriate to answer the research question!-->


Our p-value is 0.000009421. Our df value is 27.079. Our t-value is -5.4341. Our alternative hypothesis is shown. It states true differences in means between group LINE and group SKILL is not equal to 0. Our sample estimates are: mean in group LINE is 17.12500; mean in group SKILL is 49.72. If ounull hypothesis is true, the p value is the probability of getting our results. LINE vs SKILL. It is very rare. The p-value is so small we would reject (ignore) the null hypothesis. If it's greater than .05, you failed to reject the null hypothesis (that's bad). If I rject the null hypothesis, I am 95% sure the SKILL group can do more push-ups.

# Discussion and Conclusion

<!--Discussion and conclusion here. If you found a relationship be sure to consider whether the relationship occurs because one of the variavbles causes the other, or whether they perhasps are related for some other reason. Watch the chapter 6 videos from the GeorgeTown videos collection.!-->

The original question was this: "Who could do the most push-ups? The SKILL position or the LINE position under a specific amount of time?" Our response: based off of our numerical descriptive results & our inferential results. We can see that the SKILL position can do more push-ups than the LINE position under any amount of time given. We used a box plot & a table to figure out our values and percentages. The median and average were much higher for the SKILL position.